%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

% ---------------------------------------------------------
\cvsubsection{Published}
%---------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{Bayle, G.}, S. Farolfi, E. Lavaine, M. Willinger. 2023. \textit{Solving Conflicts over Common-pool Resources through Stakeholder Delegation.} in Journal of Economic Behaviors and Organizations, Vol. 227, 106702.}
\end{cvpubs}

% % %---------------------------------------------------------
% \cvsubsection{In Review}
% % %---------------------------------------------------------

% \begin{cvpubs}
%     \cvpub{\textbf{Bayle, G.}, E. Lavaine, S. Farolfi, M. Willinger. 2023. \textit{Solving Conflicts over Common-pool Resources through Stakeholder Delegation.} \textbf{Revise and resubmit} in Journal of Economic Behaviors and Organizations (JEBO)}
% \end{cvpubs}

% %---------------------------------------------------------
\cvsubsection{Submitted}

\begin{cvpubs}
\small \color{black}
    \cvpub{\textbf{Bayle, G.}, M. Willinger. 2025. \textit{Efficiency of the Minimum Approval Mechanism with heterogeneous players.} R\&R in Journal of Public Economic Theory}   

    \cvpub{\textbf{Bayle, G.}, D. Dubois, M. Willinger. 2025. \textit{L'économie à l'ère de la science ouverte : un nouvel élan pour la reproductibilité.}}  
\end{cvpubs}

\cvsubsection{In Prep}
% %---------------------------------------------------------

\begin{cvpubs}
\small \color{black}
    
    \cvpub{\textbf{Bayle, G.} \textit{Four ways to share a pie: Identifying distributional preferences with machine learning.}}

    \cvpub{\textbf{Bayle, G.}, N. Quérou, M. Beaud, D. Dubois, M. Willinger. \textit{Mobile common pool resources: Theory and experiment on resource-users behaviors.}}

    \cvpub{Bobin, N., \textbf{G. Bayle}, D. Dubois, M. Willinger. \textit{Overconfidence and competitiveness: A lab-in-the-field experiment.}}

    \cvpub{Belard, A., D. Jourdain, S. Farolfi, \textbf{G. Bayle}. \textit{Enhancing cooperation between farmers in Zimbabwe: A Threshold Public good lab-in-the-field experiment.}}

    \cvpub{\textbf{Bayle, G.}, Y. Funaki. \textit{Studying cooperative bargaining with non-cooperative disagreement options.}}

    \cvpub{\textbf{Bayle, G.}, V. Pham, Y. Kamijo. \textit{Bargaining under social dilemmas and risk: An experimental approach on binding and non-binding agreements in dynamic CPR dilemmas.}}

    \cvpub{\textbf{Bayle, G.}, V. Pincon, G. Barragan-Jason, C. Bazart, D. Dubois, L. Ibanez, S. Roussel, A. Syssau-Vaccarella, M. Willinger. \textit{Inter-generational common pool resources: Priming, Perspectives and Transmission.}}

    
\end{cvpubs}

% %---------------------------------------------------------
